Neural Neural Textures Make Better Simulators ``I Can't Believe It's Not Real!''

### 2022-06-16 CORL/example.tex

\begin{abstract}
	% Abstracts should be a single paragraph, between 4--6 sentences long, ideally. Gross violations will trigger corrections at the camera-ready phase.
	% Because of the 6 sentence limit, I've commented out some of the sentences...
	Unpaired image translation algorithms can be used for sim-to-real tasks, but most fail to generate temporally consistent results.
	% Because of this, the details or even identity of a particular object might change as it moves across a scene.
	We present a new approach that combines differential rendering with image translation to achieve temporal consistency over indefinite timescales.
%
	%TURNING TWO SENTENCES INTO ONE:
	% We call this algorithm TRITON (Texture Recovering Image Translation Network): an unsupervised, end-to-end, stateless sim-to-real algorithm.
	% Unlike previous techniques, TRITON leverages the underlying 3d geometry of input scenes by generating realistic-looking learnable neural textures.
	We call this algorithm TRITON (Texture Recovering Image Translation Network): an unsupervised, end-to-end, stateless sim-to-real algorithm that 
	leverages the underlying 3d geometry of input scenes by generating realistic-looking learnable neural textures.
%
	% These textures are projected onto the surfaces of input scenes, which are then fed through an image translation network to obtain the final outputs.
	By settling on a particular albedo for the objects in a scene, we ensure consistency between frames statelessly.
	Unlike previous algorithms, TRITON is not limited to camera movements - it can handle the movement of objects as well, making it useful for downstream tasks such as robotic manipulation.
	Our experiments show that in addition to achieving higher temporal consistency, the translations are closer to ground truth photographs than previous techniques.
\end{abstract}
\keywords{sim to real, image translation, differentiable rendering}

@@

%===============================================================================
\section{Formulation}
\label{sec:data}
	\begin{figure}[H]
	\vspace{-10pt}
		\begin{center}
			\includegraphics[width=400pt]{../images/first_diagram.pdf}
		\end{center}
		\vspace{-5pt}
		\caption{
			This is an overview of what TRITON accomplishes.
			TRITON learns the textures of 3d objects to help translate simulated images into photographs. It does this with unpaired data. Each row is a different dataset.
			}
		\label{fig:first_diagram}
	\end{figure}
	% TRITON stands for Texture Recovering Image Translation Network. It has two goals: to translate images, and to recover textures.

@@

		To keep the object surfaces consistent between a batch of $N$ outputs, we impose a pixel-wise ``unprojection consistency loss'' between these surfaces by unprojecting them back into a common texture space.
		\begin{equation}
			u\toNL=\text{unproject}(\ph\toN,s\toN)   \eqand  \lUC \Rightarrow u_1 \approx u_2 \dots \approx u_N
		\end{equation}

		We sample a random batch of UVL scenes $S\toN$, and translate them into $\ph\toN$.
		Using geometric knowledge of the scene encoded in $S\toN$, we individually unproject each $\ph^i \in \ph\toN$ back into texture space, to obtain $N$ sets of $L$ unprojected textures $u\toNL$.
		We then use the per-pixel, batch-wise standard deviation of the unprojections as unprojection consistency loss $\lUC = \sigma(u\toNL)\toL$.
		This loss observes how different these unprojections are from one another, and thus how different the object surfaces appear between translations.

@@

		% %Unabbreviated
		% \begin{equation}
		% 	\unprojection_{c,U,V}^{n,i}=\expectation\ph_{c,x,y}^n 
		% 	\eqand \bar{\unprojection}^i_{c,u,v}   =   
		% 		\frac{1}{N} \lsum_{n=1}^N\unprojection^{n,i}_{c,u,v} 
		% 	\eqand 
		% 	\lUC=\frac{\lsum_{i=1}^L\lsum_{c=1}^3\lsum_{U=1}^{128}\lsum_{V=1}^{128}
		% 	\sqrt[]{\frac{1}{N}\lsum_{n=1}^N\left(\bar{\unprojection}^i_{c,u,v}-\unprojection^{i,n}_{c,U,V}\right)^2}}
		% 	{3\cdot128\cdot128\cdot L}
		% \end{equation}
		%
		%Abbreviated
		To formally define $\lUC$ we define unprojections $\unprojection^{1...N,1...L}$ and mean unprojections (aka recovered textures) $\bar{\unprojection}^{1...L}$ 
		with each $\unprojection^{n,i}\in\real^{3\times128\times128}$:
		\begin{equation}
			\unprojection_{U,V}^{n,i}=\expectation\ph_{x,y}^n 
			\eqand \bar{\unprojection}^i_{u,v}   =   
				\frac{1}{N} \lsum_n\unprojection^{n,i}_{u,v} 
			\eqand 
			%\lUC=\frac{\lsum_{i,U,V}
			%\sqrt[]{\frac{1}{N}\lsum_n\left(\bar{\unprojection}^i_{u,v}-\unprojection^{i,n}_{U,V}\right)^2}}
			%{128\cdot128\cdot L}
			\lUC=\mathbb{E}\left[
			\sqrt[]{\frac{1}{N}\lsum_n\left(\bar{\unprojection}^i_{u,v}-\unprojection^{i,n}_{U,V}\right)^2} \right]
		\end{equation}
		where $U=\lfloor128u\rfloor$ and $V=\lfloor128v\rfloor$ and $i=I(l)$ with
		%  $(u,v,l)=s^n_{1...3,x,y}$
		$u=s^n_{1,x,y}$, $v=s^n_{2,x,y}$, $l=s^n_{3,x,y}$
		for all 
		$n \in \{1...N\}$ , 
		$i \in \{1...L\}$ , 
		$x \in \{1...W\}$ , 
		$y \in \{1...H\}$ , 
		$U \in \{1...128\}$ , 
		$V \in \{1...128\}$.

	\subsection{Texture Realism Loss}
	\label{sec:texture_realism_loss}
        \vspace{-12pt}
		\begin{figure}[thbp]
			\begin{center}
				\includegraphics[width=250pt]{../images/texture_realism_ablation.pdf}
			\end{center}
			\vspace{-5pt}
			\caption{
				The neural texture looks more realistic with texture realism loss enabled. Note that the blocks show different letters because of different initializations and the symmetry of a cube - both solutions are valid texture assignments. 
			}
			\vspace{-10pt}
			\label{fig:texture_realism_ablation}
		\end{figure}

@@

\subsection{Qualitative Evaluation Results}
\begin{figure}[thbp]
    \vspace{-30pt}
	\begin{center}
		\includegraphics[width=\textwidth]{../images/frame_inconsistency_diagram.pdf}
	\end{center}
	% Each outline color corresponds to the same cube.
	% The same cubes are marked with the same colored outlines across all photos.
	% For the same cube, we expect to see the same number on the top of the cube regardless of its placement.
	\caption{
		Each row of images shows a different random placement of objects in the scene.
		Each column of images is a different image translation algorithm.
		The same cube is marked with the same color outline across all photos.
		TRITON is consistent: for example, the cube outlined as yellow always has an 8 on the top.
		Meanwhile, CycleGan for example shows a 4 on the top of that cube in the top two rows, but an 8 and a 7 in the next two rows.
		Because of the symmetry of the cubes, and the unsupervised training, it is arbitrary which synthetic cube gets which symbol after training - but whatever it chooses, it should be consistent between placements.
		CUT and CycleGan are not consistent, while TRITON is.
		% TODO: Update the images in this to have the latest training iteration...
		}
		\label{fig:frame_inconsistency_diagram}
	\end{figure}

@@

	%CREATED WITH https://www.tablesgenerator.com/# -- this website is wonderful!!
\begin{table}[H]
    \caption{Ground truth comparison evaluations for TRITON. Masked and Unmasked mean xxxxxx. Sync and Unsync mean xxxxx. L2 is xxxx LPIPS is xxxxxx. TRITON is xxxxxxx. }
	\resizebox{\textwidth}{!}{
        \begin{tabular}{lcccccccc}
        \toprule
        & \multicolumn{4}{c}{Masked} & \multicolumn{4}{c}{Unmasked}  \\
        \cmidrule(lr){2-5} \cmidrule(lr){6-9} & \multicolumn{2}{c}{LPIPS ($\times 10^{-1}$) $\downarrow$} & \multicolumn{2}{c}{L2 ($\times 10^{-2}$) $\downarrow$}  & \multicolumn{2}{c}{LPIPS ($\times 10^{-1}$) $\downarrow$}  & \multicolumn{2}{c}{L2 ($\times 10^{-2}$) $\downarrow$}   \\
        \cmidrule(lr){2-3} \cmidrule(lr){4-5} \cmidrule(lr){6-7} \cmidrule(lr){8-9}
        Algorithm  & Sync    & Unsync   & Sync      & Unsync    & Sync   & Unsync  & Sync     & Unsync \\
        \midrule
        TRITON w/o $\psi, \lUC, \lTR$ & 0.437                        & 0.373                        & 0.500                        & 0.490                        & 4.34                        & 4.02                        & 4.25                        & 3.92                        \\
        TRITON w/o $\lUC, \lTR$       & 0.442                        & 0.386                        & 0.586                        & 0.589                        & 2.85                        & 2.55                        & 3.64                        & 3.10                        \\
        \textbf{TRITON}                        & \textbf{0.286}               & \textbf{0.267}               & \textbf{0.479}               & \textbf{0.478}               & \textbf{1.17}               & \textbf{1.16}              & \textbf{1.23}               & \textbf{1.22}               \\
        \midrule
        CycleGAN & 0.450 & 0.379 &  0.559 &  0.554 &  6.02 &  5.93 &  4.25 &  4.23 \\
        CUT                           & 0.469                        & 0.382                        & 0.553                        & 0.526                        & 5.40                        & 5.34                        & 6.37                        & 6.29\\
        \bottomrule
        \end{tabular}
	}
\end{table}

>>>>

\begin{abstract}
	% Abstracts should be a single paragraph, between 4--6 sentences long, ideally. Gross violations will trigger corrections at the camera-ready phase.
	% Because of the 6 sentence limit, I've commented out some of the sentences...
	Unpaired image translation algorithms can be used for sim-to-real tasks, but most fail to generate temporally consistent results.
	% Because of this, the details or even identity of a particular object might change as it moves across a scene.
	We present a new approach that combines differential rendering with image translation to achieve temporal consistency over indefinite timescales.
%
	%TURNING TWO SENTENCES INTO ONE:
	% We call this algorithm TRITON (Texture Recovering Image Translation Network): an unsupervised, end-to-end, stateless sim-to-real algorithm.
	% Unlike previous techniques, TRITON leverages the underlying 3d geometry of input scenes by generating realistic-looking learnable neural textures.
	We call this algorithm TRITON (Texture Recovering Image Translation Network): an unsupervised, end-to-end, stateless sim-to-real algorithm that 
	leverages the underlying 3d geometry of input scenes by generating realistic-looking learnable neural textures.
%
	% These textures are projected onto the surfaces of input scenes, which are then fed through an image translation network to obtain the final outputs.
	By settling on a particular albedo for the objects in a scene, we ensure consistency between frames statelessly.
	Unlike previous algorithms, TRITON is not limited to camera movements --- it can handle the movement of objects as well, making it useful for downstream tasks such as robotic manipulation.
	Our experiments show that in addition to achieving higher temporal consistency, the translations are closer to ground truth photographs than previous techniques.
\end{abstract}
\keywords{sim to real, image translation, differentiable rendering}

@@

%===============================================================================
\section{Formulation}
\label{sec:data}
	\begin{figure}[thbp]
	\vspace{-10pt}
		\begin{center}
			\includegraphics[width=\textwidth]{../images/first_diagram.pdf}
		\end{center}
		\vspace{-5pt}
		\caption{
			This is an overview of what TRITON accomplishes.
			TRITON learns the textures of 3d objects to help translate simulated images into photographs. It does this with unpaired data. Each row is a different dataset.
			}
		\label{fig:first_diagram}
	\end{figure}
	% TRITON stands for Texture Recovering Image Translation Network. It has two goals: to translate images, and to recover textures.

@@

		To keep the object surfaces consistent, we impose a pixel-wise ``unprojection consistency loss'' by unprojecting surfaces in fake photos back into the common texture space.
% 		\begin{equation}
% 			u\toNL=\text{unproject}(\ph\toN,s\toN)   \eqand  \lUC \Rightarrow u_1 \approx u_2 \dots \approx u_N
% 		\end{equation}
        Given a UVL scene $s$ and its respective fake photo $\ph$, the unprojection $\unprojection$ is obtained from assigning $(r,g,b)$ values at each pixel location $(x, y)$ of $\ph$ to its corresponding $(u, v, l)$ coordinates according to $s$. 
        % That is, we convert $s$ and $\ph$ to a key-value dictionary where the key is $(u,v,l)$ and the value is $(r,g,b)$, and such dictionary is $\unprojection$.
        For simplicity, we note
        \begin{equation}
            	\unprojection_{[u,v]}^{l}=\expectation\ph_{[x,y]} \quad s.t.~ (u,v,l) = s_{[x,y]},
        \end{equation}
        where the expectation $\mathbb{E}$ means we aggregate multiple $(r,g,b)$ vectors being assigned to the same $(u,v,l)$ location by averaging them. 
        In practice, $(u,v,l)$ are real numbers between $[0,1]$, where as each $\unprojection$ have to be rasterized, i.e represented by $L$ $(128\times 128\times 3)$ images, where $L$ is the number of labels and $128\times 128$ is the resolution of the unprojection. Therefore, we discretize and scale corresponding $(u,v,l)$ to integers so that each $(r,g,b)$ vector will be assigned to a pixel on $\unprojection$. For the exact implementation, please see our supplementary material.

        We obtain $N$ unprojections $\{\unprojection_{[u,v]}^{l,i}\}_{i=1}^{N}$ from a batch of $N$ UVL scenes and fake photos. The unprojection consistency loss is defined as the per-pixel
        \begin{equation}

        \end{equation}

		%We sample a random batch of UVL scenes $S\toN$, and translate them into $\ph\toN$.
		%Using geometric knowledge of the scene encoded in $S\toN$, we individually unproject each $\ph^i \in \ph\toN$ back into texture space, to obtain $N$ sets of $L$ unprojected textures $u\toNL$.
		%We then use the per-pixel, batch-wise standard deviation of the unprojections as unprojection consistency loss $\lUC = \sigma(u\toNL)\toL$.
		%This loss observes how different these unprojections are from one another, and thus how different the object surfaces appear between translations.

@@

		% %Unabbreviated
		% \begin{equation}
		% 	\unprojection_{c,U,V}^{n,i}=\expectation\ph_{c,x,y}^n 
		% 	\eqand \bar{\unprojection}^i_{c,u,v}   =   
		% 		\frac{1}{N} \lsum_{n=1}^N\unprojection^{n,i}_{c,u,v} 
		% 	\eqand 
		% 	\lUC=\frac{\lsum_{i=1}^L\lsum_{c=1}^3\lsum_{U=1}^{128}\lsum_{V=1}^{128}
		% 	\sqrt[]{\frac{1}{N}\lsum_{n=1}^N\left(\bar{\unprojection}^i_{c,u,v}-\unprojection^{i,n}_{c,U,V}\right)^2}}
		% 	{3\cdot128\cdot128\cdot L}
		% \end{equation}
		%
		%Abbreviated
		%To formally define $\lUC$ we define unprojections $\unprojection^{1...N,1...L}$ and mean unprojections (aka recovered textures) $\bar{\unprojection}^{1...L}$ 
		%with each $\unprojection^{n,i}\in\real^{3\times128\times128}$:
% 		\begin{equation}
% 			\unprojection_{U,V}^{n,i}=\expectation\ph_{x,y}^n 
% 			\eqand \bar{\unprojection}^i_{u,v}   =   
% 				\frac{1}{N} \lsum_n\unprojection^{n,i}_{u,v} 
% 			\eqand 
% 			%\lUC=\frac{\lsum_{i,U,V}
% 			%\sqrt[]{\frac{1}{N}\lsum_n\left(\bar{\unprojection}^i_{u,v}-\unprojection^{i,n}_{U,V}\right)^2}}
% 			%{128\cdot128\cdot L}
% 			\lUC=\mathbb{E}\left[
% 			\sqrt[]{\frac{1}{N}\lsum_n\left(\bar{\unprojection}^i_{u,v}-\unprojection^{i,n}_{U,V}\right)^2} \right]
% 		\end{equation}
% 		where $U=\lfloor128u\rfloor$ and $V=\lfloor128v\rfloor$ and $i=I(l)$ with
% 		%  $(u,v,l)=s^n_{1...3,x,y}$
% 		$u=s^n_{1,x,y}$, $v=s^n_{2,x,y}$, $l=s^n_{3,x,y}$
% 		for all 
% 		$n \in \{1...N\}$ , 
% 		$i \in \{1...L\}$ , 
% 		$x \in \{1...W\}$ , 
% 		$y \in \{1...H\}$ , 
% 		$U \in \{1...128\}$ , 
% 		$V \in \{1...128\}$.

	\subsection{Texture Realism Loss}
	\label{sec:texture_realism_loss}
        \vspace{-7pt}
		\begin{figure}[thbp]
			\begin{center}
				\includegraphics[width=250pt]{../images/texture_realism_ablation.pdf}
			\end{center}
			\vspace{-5pt}
			\caption{
				The neural texture looks more realistic with texture realism loss enabled. Note that the blocks show different letters because of different initializations and the symmetry of a cube - both solutions are valid texture assignments. 
			}
			\vspace{-10pt}
			\label{fig:texture_realism_ablation}
		\end{figure}

@@

\subsection{Qualitative Evaluation Results}
We show qualitative evaluation results 
\begin{figure}[thbp]
    \vspace{-30pt}
	\begin{center}
		\includegraphics[width=\textwidth]{../images/frame_inconsistency_diagram.pdf}
	\end{center}
	% Each outline color corresponds to the same cube.
	% The same cubes are marked with the same colored outlines across all photos.
	% For the same cube, we expect to see the same number on the top of the cube regardless of its placement.
	\caption{
		Each row of images shows a different random placement of objects in the scene.
		Each column of images is a different image translation algorithm.
		The same cube is marked with the same color outline across all photos.
		TRITON is consistent: for example, the cube outlined as yellow always has an 8 on the top.
		Meanwhile, CycleGan for example shows a 4 on the top of that cube in the top two rows, but an 8 and a 7 in the next two rows.
		Because of the symmetry of the cubes, and the unsupervised training, it is arbitrary which synthetic cube gets which symbol after training - but whatever it chooses, it should be consistent between placements.
		CUT and CycleGan are not consistent, while TRITON is.
		% TODO: Update the images in this to have the latest training iteration...
		}
		\label{fig:frame_inconsistency_diagram}
	\end{figure}

@@

	%CREATED WITH https://www.tablesgenerator.com/# -- this website is wonderful!!
\begin{table}[thbp]
    \caption{Ground truth comparison evaluations for TRITON. Masked and Unmasked mean xxxxxx. Sync and Unsync mean xxxxx. L2 is xxxx LPIPS is xxxxxx. TRITON is xxxxxxx. }
	\resizebox{\textwidth}{!}{
        \begin{tabular}{lcccccccc}
        \toprule
        & \multicolumn{4}{c}{Masked} & \multicolumn{4}{c}{Unmasked}  \\
        \cmidrule(lr){2-5} \cmidrule(lr){6-9} & \multicolumn{2}{c}{LPIPS ($\times 10^{-1}$) $\downarrow$} & \multicolumn{2}{c}{L2 ($\times 10^{-2}$) $\downarrow$}  & \multicolumn{2}{c}{LPIPS ($\times 10^{-1}$) $\downarrow$}  & \multicolumn{2}{c}{L2 ($\times 10^{-2}$) $\downarrow$}   \\
        \cmidrule(lr){2-3} \cmidrule(lr){4-5} \cmidrule(lr){6-7} \cmidrule(lr){8-9}
        Algorithm  & Sync    & Unsync   & Sync      & Unsync    & Sync   & Unsync  & Sync     & Unsync \\
        \midrule
        TRITON w/o $\psi, \lUC, \lTR$ & 0.437                        & 0.373                        & 0.500                        & 0.490                        & 4.34                        & 4.02                        & 4.25                        & 3.92                        \\
        TRITON w/o $\lUC, \lTR$       & 0.442                        & 0.386                        & 0.586                        & 0.589                        & 2.85                        & 2.55                        & 3.64                        & 3.10                        \\
        \textbf{TRITON}                        & \textbf{0.286}               & \textbf{0.267}               & \textbf{0.479}               & \textbf{0.478}               & \textbf{1.17}               & \textbf{1.16}              & \textbf{1.23}               & \textbf{1.22}               \\
        \midrule
        CycleGAN & 0.450 & 0.379 &  0.559 &  0.554 &  6.02 &  5.93 &  4.25 &  4.23 \\
        CUT                           & 0.469                        & 0.382                        & 0.553                        & 0.526                        & 5.40                        & 5.34                        & 6.37                        & 6.29\\
        \bottomrule
        \end{tabular}
	}
\end{table}
